FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-08-15 paper.tex
Work from second column

\Fp{} provides a finite approximation of the real numbers in a format that is efficient for calculation on a computer.
IEEE 754~\cite{IEEEStandardBinary1985} standardizes \fp{} representation and operations---these days, most machines and languages follow the IEEE 754 standard, and we make no effort to generalize our work beyond what IEEE 754 specifies.

\Fp{} is essentially scientific notation---\fp{} numbers are represented by packing a sign bit, an exponent, and an fraction part (also called the ``significand'' or ``mantissa'') into contiguous bit fields.
The advantages of this representation are that allows for compact representation of both very small and very large numbers in a narrow range of bits---a 64-bit float can represent numbers as big as $2^{1024}$ and as small as $2^{-1074}$.
This range is sufficient to represent numbers as small as Planck's constant or as big as Avogadro's constant with reasonable accuracy.

@@

>>>>

\Fp{} provides a finite approximation of the real numbers in a format that is efficient for calculation on a computer.
\Fp{} is essentially scientific notation---\fp{} numbers are represented by packing a sign bit, an exponent, and a fraction part (also called the ``significand'' or ``mantissa'') into contiguous bit fields.
The advantages of this representation are that allows for compact representation of both very small and very large numbers in a narrow range of bits---a 64-bit float can represent numbers as big as $2^{1024}$ and as small as $2^{-1074}$.
This range is sufficient to represent numbers as small as Planck's constant or as big as Avogadro's constant with reasonable accuracy.

@@

IEEE 754~\cite{IEEEStandardBinary1985} standardizes \fp{} representation and operations---these days, most machines and languages follow the IEEE 754 standard, and we make no effort to generalize our work beyond what IEEE 754 specifies.
